Molecular Gas Kinematics of the Strongly-Lensed Quasar Host Galaxy RXS J1131$-$1231

### 2016-11-18 WRITEUP/response.md

We thank the referee for providing constructive and thoughtful
comments to improve the manuscript. We have addressed all the concerns
raised by the referee and details can be found in the revised version of the manuscript -- please see attached. A brief description on how we incorporated the referee's suggestions can be found below.

COMMENTS IN DETAIL:

1) TOO MANY "DYNAMICS" AND "DYNAMICAL".

You may be mis-using the word "dynamical" in some places.
"Dynamics" refers to the effects of a force, or forces, in 
causing motions, or in reaching equilibrium.

So if you are mainly talking about velocities, it would be 
better to say "velocities" or "kinematics" instead of "dynamics".

1a): CHANGE THE TITLE : DROP THE WORD "DYNAMICS" :

The Title says the paper is about the "dynamics" of the molecular gas in the 
quasar host galaxy.

Most of the paper, however, is not about the "dynamics" at all, 
but rather about the CO detections,
the VLA continuum map (synchrotron emission, not molecular gas), 
the spectral energy distribution in the optical, near-IR, mid-IR, and far-IR continuum,
and the gravitational lens model.

I suggest that you consider changing the title, to better describe the
contents of the paper, maybe something like:

"CO-Line, Radio Continuum, Optical-to-Far-IR Observations, and Lens Models of
the Host Galaxy of the Quasar RXS J1131-1231"

or maybe:

"Interpretation of CO, Radio, Optical, and IR Continuum 
observations of the Strongly Lensed Host Galaxy of the 
Quasar RXS J1131-1231"

or simply:

"CO, Radio, Optical, and IR results on 
the Lensed Host Galaxy of the Quasar RXS J1131-1231".

# RESPONSE:
1a) We have changed the title to "Molecular gas kinematics of the strongly lensed quasar host galaxy RXSJ1131-1231".
We agree that we study more than just the CO gas of the science target in this paper; however, a large fraction of the paper is based on our new CO data and the analysis (incl. lens modeling). Therefore, we think that the title is suitable for the paper.

@@

The literature/archival data of the continuum would not be as meaningful without our CO data, e.g. their emission does not convey inforamtion about the kinematics, spatial distribution, and does not give a broader picture regarding the f_gas evolution, which is one of the main conclusions found in this study.

1b) DROP "DYNAMICALLY RESOLVED":

Sect.3.1, paragraph 1:

"The emission is spatially and dynamically resolved...as shown in Fig. 1 "

"Dynamically resolved" sounds strange. 
The reader might confuse it with the dynamic range.
Maybe change to :

"The line emission is resolved, in both velocity (Fig. 1) and 
in its spatial distribution (Fig. 2).

# RESPONSE:
We took this suggestion. To minimize potential confusion, we have changed "dynamically resolved" to "kinematically resolved".

1c) DROP "DYNAMICAL CENTER":

Fig.3, caption:
"...z = 0.6537, which corresponds to the dynamical center of CO(2-1)."

Change to :

"..which corresponds to zero velocity in the CO(2-1) spectum (Fig.1)."

# RESPONSE:
We took this suggestion and have updated our redshift (and re-plotted the figure) based on the results from fitting a double-Gaussian to the de-lensed intrinsic line profile of our target (Fig. 5).

1d): DROP "RECONSTRUCT THE DYNAMICS" :

Sect.4.1, para.1:

Too many "dynamics" in this paragraph.

"...the high spectral resolution .. provides dynamical information 
on scales smaller than the beam ..."

Maybe change to "velocity information" or "kinematic information".

"...we reconstruct the intrinsic gas dynamics by carrying out 
lens modeling over different channel slices..."

You are not reconstructing the "dynamics", 
you are reconstructing the intrinsic spectral profile, by separately 
deriving the lens magnifications in seven different velocity channels.

As you say in the Abstract, this shows that the asymmetric line profile
(red peak stronger than blue peak) is actually symmetric.

I don't think this is reconstructing the "dynamics."
The "dynamics" stays the same --- rotation in a gravitational force field.

You have just reconstructed the line shape, that's all.

Contrary to what you say in Sect.4.1, this is actually not 
"similar" to the "differential lensing ...across the HST V, I and H bands (Claeskens+ 2006)

They talk about different magnification due to varying sizes of different temperature regions.
In the Claeskens reconstruction, the blue light (redshifted to V band) comes from young hot stars 
in a nuclear starburst ring --- see their sect.5.2, point 4.

The V-band source is smaller (more compact) than the cooler regions in I and H bands,
in the larger spiral disk farther from the nucleus.

So, they interpret the different magnifications as due to different sizes in the source plane.

This is not the same as magnification varying across the line profile,
due to different source-plane positions, as you are claiming.

# RESPONSE:
We took this suggestion and have changed "dynamical information" to "kinematic information", "reconstruct the intrinsic gas dynamics" to "reconstruct the intrinsic line profile and source-plane velocity structure".

@@

We have rephrased the 2nd paragraph of Sec 4.1.2 to clarify what we meant.

2) FIX THE REDSHIFT. IT SHOULD BE 0.6541 .

Your beautiful CO(2-1) spectrum gives the best measurement 
so far of the qso host galaxy redshift,
more precise than the optical spectra.

For this reason, you should make a little extra effort to get it exactly right.

2a. OBSERVED FREQUENCY, NOT LO FREQUENCY.

Sect.2.1, para. 1:

You say nu_LO = 139.256 GHz.
But this is your observed frequency, not the LO frequency.
It corresponds to CO(2-1) redshifted to 0.6555.

What probably happened was this:

a) You say that you first observed at CARMA (Feb.2014).
At CARMA, your sensitivity was only good enough to see the red peak, and not the blue one.
From the CARMA data, you derived the wrong redshift of z = 0.6555.

b) You say that you then observed at IRAM (later, in Dec.2014 and Feb.2015).
Because you already had the (incorrect) redshift from CARMA, 
you set the IRAM observing frequency to the wrong redshift of 0.6555 (139.256 GHz),

Then, with the better sensitivity at IRAM, you discovered that the true line profile 
was actually centered closer to z = 0.6537 (139.4074 GHz).

c) Later on, you re-reduced the data, this time with zero velocity corresponding 
to z = 0.6537, for all the figures in this paper.

d) But your Fig.1 (CO 2-1 spectrum), and especially, 
Fig.5 (both spectra, yellow and blue histograms),
show clearly that the line centroid is at +75 km/s relative to zero velocity.

e) At redshifted CO(2-1), there are 2.15 km/s per MHz, so the true line centroid 
is 34.88 MHz lower than your assumed zero frequency, and 
so the true line centroid is at 139.373 GHz.

f) This corresponds to z = 0.6541, as the true redshift of the host galaxy.

g) SUGGESTED CHANGES :

Sect.3.1, para.1: 
"...confirming the redshift at z = 0.6537..."

--- change to:
"...showing that the line centroid is at a redshift of z = 0.6541..."

Fig.3 caption:
"The velocity scale is with respect to z=0.6537, which corresponds to the dynamical center..."

--- change to:
"The zero of the velocity scale is at z=0.6537, which is close to the 
true centroid of the CO(2-1) line at z=0.6541 ...

Sect.4.5 para.2:

---Possibly re-do the fit, relative to a zero velocity at z = 0.6541, as this will change
the V_max in your p-v diagram (Fig.9, right panel).

--- Or else just explain that the V_0 in your Eq(1) comes out to +28 km/s (relative to z=0.6537)
because of the very coarse sampling of your seven 108 km/s-wide bins.

The true line center (relative to z=0.6537) would be at V_0 = +75 km/s if you had
used the full-resolution spectrum (Fig. 1 or Fig.5), rather than the heavily binned channels.

# RESPONSE:
We have corrected nu_LO --> nu_obs.

We took this suggestion and re-fitted a doubled Gaussian to the de-lensed profile (Fig. 5) and updated the redshift and replotted all the relavent figures (and updated their captions correspondingly), updated column 1 in Table 3, the labeling in Fig 7, refitted the model shown in Fig. 9 and updated parameters in Sec 4.3 correspondingly, SED fitting, etc.

3) CO(2-1) FLUX AND SOURCE SIZE :

Sect. 3.1, para.1: CO(2-1) LINE FLUX :

You say the 2-Gaussian fit gives :
red peak = 75.3 mJy (do you mean mJy/beam?), FWHM=179 km/s,
and blue peak = 24 mJy (do you mean mJy/beam?), FWHM = 255 km/s.

This gives 1.06 x 75.3 x 179 /1000 = 14.3 Jy km/s for the red peak,
and gives 1.06 x 24.1 x 255 /1000 = 6.5 Jy km/s for the blue peak.

So the sum of the two peaks is 20.8 Jy km/s, not the value of 24.1 Jy km/s in the text.

Or, are the values you quote for two Gaussian components only the values at the top pixel of the map?
That is, not spatially integrated, while the 24.1 Jy km/s is spatially integrated?
You need to make this clear, both in the text, and in the caption to Fig.1.

If Fig.1 shows only the spectrum at the source maximum, and not the 
spatially integrated spectrum, then you need to change the label on the vertical axis 
to Flux density per beam [ mJy /beam ].

In the re-plot of the CO(2-1) spectrum that you give in Fig.5 (yellow histogram),
the redshifted peak is now 100 mJy, not 75, as in Fig.1.

Does Fig.5 now show the spatially integrated spectrum ? 
What is the difference between this spectrum and the one in Fig.1?

If it is again a spectrum taken at the maximum-intensity point,
then the units on the vertical axis would again have to be [ mJy/beam ].

In Fig.5,it would be good to show what you think is the contribution from the companion galaxy.

# RESPONSE:
We found a bug in generating the map used for previous line-integrated flux extraction. In the resubmitted version, we have updated the intensity reported for CO(2-1) by summing the fluxes in the relavent channels, which is in agreement with the double-Gaussian fit to the spatially extracted spectrum (Fig. 1). Since our lensing-corrected M_gas for both RXJ1131 and the companion are derived from the flux in each channel, this doesn't change our conclusion.

@@

We tried adding the companion's spectrum to plot (Fig. 5) but found the figure to be over-crowded/too busy, as there are already showing various things with different various linestyles, colors. This main message for this plot is to show that we find that the intrinsic profile of the main galaxy is symmetric, which is informative about the kinematics of this galaxy. On the other hand, the useful info for the companion from the de-lensed spectrum is the gas mass, which we report in the text (and in the table, as suggested by the referee).

Sect. 3.1, para.3: SOURCE SIZE :

I don't think you can measure source size to three significant figures,
especially if you measure the beam-smoothed sizes in the image plane,
and then try to estimate the deconvolved sizes by doing root square
subtraction of the beam sizes (if that's what you did).

An advantage of an interferometer is that you can 
do fits to the source size in the u,v plane, without having
to deconvolve the beam.

Because the whole process is uncertain, 
instead of saying " 5.1 +/- 0.72 by 3.72 +/- 0.66 ",
you could just say 5.1 +/- 0.7 by 3.7 +/- 0.7 .

This is especially true because you say in the next sentence, that the 
emission is not a 2-D Gaussian, so the fitted model is anyway 
not correct.

But an even bigger problem is that these values look like the observed (not deconvolved)
major and minor axis sizes (FWHM) on the integrated map in Fig.2 (upper left).

Are you sure that you have deconvolved these sizes? For a 4.4" x 2" beam?

Please check this.

Even better, try doing a fit in the u,v plane, rather than the sky plane.

Here's another problem with the source size:
In Sect.1, para.3, you say the stellar emission in the host galaxy of RXJ1131 is 
lensed into an Einstein ring of radius 1.83" (diameter = 3.66"). 
So the length of the arc is about 4 or 5 arcsec.

In Table 3, you say the median magnification is a factor of 5.5.

This means the de-magnified CO source DIAMETER is about 1 arcsec.

At z = 0.654, 1 arcsec is 7 kpc.

So the de-magnified RADIUS of the CO source is only 3.5 kpc.

It looks like the intrinsic R_CO = 6 kpc (diameter = 12 kpc)
that you quote elsewhere in the paper is too high:
---Abstract, 
---Sect.4.3, para.3, 
---Sect.4.4, para.1, 
---Sect.5.1.1, para.2,
---Sect.5.5, para.2
---Sect.5.1.1, para.2,
---Sect.6, para.2

# RESPONSE:
Source size: We fitted a single Guassian in uv-plane to support the reported CO size based on image plane fitting, of which the convolved size is 6.6+/-0.5 x 4.5+/-0.3. We additionally report the source sizes by fitting two Gaussians to provide further evidence that the CO(2-1) emission is resolved. We have updated Section 3.1 to clarify the discussion.

@@

CO physical size:
The rough estimate of de-magnified CO diameter provided in the referee report is flawed since it assumes the magnification factor to be constant along the arc. The fact that 
1) the lensed emission is not uniformly stretched along the arc (and contains complex structures within the arc)
2) CO is immune to dust extinction, therefore likely to be more extended than the optical emission, as supported by our deconvolved CO source size and in Fig. 7 (where the blue wing centroid is further out than the lensed arc), and from the results of our lens models 
indicates the CO source size is unlikely to be R ≤ 3.5 kpc.

The reported R_CO = 6 kpc is obtained based on the most extended kinematic component is consistent, see Sec 4.3.

4) ERRORS ON CO(3-2):

Sect. 3.2, para 1: 
"We detect CO(3-2) ... in the CARMA data at > 5 sigma significance."(Fig.3).

Something is wrong here. In Fig.3, the peak-to-peak noise 
in 36 km/s channels, is 100 mJy/beam. 
This means 1 sigma is 25 mJy/b.

This disagrees with Sect.2.2, para.3, which says 1 sigma is 
only 13.3 mJy/b in 36 km/s (25 MHz).

So, while the positive-velocity peak in Fig.3 is 4 or 5-sigma,
the negative velocity peak is only 2 or 3-sigma, so not really significant.

Without knowledge of the CO(2-1) spectrum,
the negative-velocity peak at CO(3-2) could not be called a real detection.

Maybe change the first sentence of Sect.3.2 to read:

"We detect CO(3-2) ... in the CARMA data at 5-sigma significance
on the positive-velocity peak. 
Within the noise limits, the CO(3-2) spectrum (Fig.3) may be
consistent with the double-peak profile seen in CO(2-1) (Fig.1)."

Because of the large errors in the CO(3-2) flux, you should not
quote the flux and the errors to three significant figures (Sect. 3.2).

Instead of saying "35.7 +/- 21.9, 
you could just say 36 +/- 22 .

Similarly, in the same paragraph, for the (3-2) / (2-1) ratio,
you could just say 0.7 +/- 0.4 .

In Sect.3.2, para.1, you say the observing frequency is 209 GHz.
So the wavelength is 1.4mm, not 1.5mm. 
(There are two places to fix this).

#RESPONSE
While the most extreme peak to peak noise is ~100 mJy/beam, the noise varies across channels, and therefore, on average, sigma is lower across all channels. Thus, the uncertainty is more representative using those obtained from the integrated map.

@@

To demonstrate that our S/N are real regardless of the fainter blue wing, we have independently obtained SNR map to confirm our results, where the peak flux in the red peak is 11.46+/-1.95 Jy/B and the blue peak is 5.13 +/- 1.45 Jy/B. 
I think what was confusing was the reported I_CO(3-2)=35.7+/-21.3Jy km/s, for which I missed a sqrt, and it should have been 35.7+/-6.91 Jy km/s, which has been corrected.

Since both CO lines are observed towards the same source, using prior knowledge about the blue wing from the CO(2-1) data to inform about the CO(3-2) emission is reasonable.

While the additioanl figure in I_CO is not significant, we keep this 
to enable reproducible results and to minimize cumulative errors (e.g. when compiled for a larger number of samples). We only report significant figures when reporting the physical parameters.

5) ERRORS ON THE 2MM CONTINUUM FLUX OF RXJ 1131:
Sect. 3.3, para.1:
The wavelengths should be 1.4mm for the CARMA data (not 1.5mm),
and 2.2mm for the IRAM data.

Sect.3.3, para.2: 
"We adopt 0.39 +/- 0.08 mJy as the 2mm continuum ...."

But Table 1 lists "0.400 +/- 0.082 " as the flux.

Both of these entries are wrong.

In Sect.3.3, para.2, you say :

integrated flux = 1.2 +/- 0.2 mJy, 
peak flux = 0.8 +/- 0.09 mJy/b at the lensing galaxy. (round off the 0.799 +/- 0.088).

You subtract a model point source at the lensing galaxy.

This gives a residual of (1.2 - 0.8) = 0.4 mJy.

But since this is a subtraction, you have to add the errors 
in the integrated flux (0.2 mJy)
to the errors in the possible point source (0.09 mJy) to get
the total uncertainty range in the residual.

So the flux of the residual is 0.4 +/- 0.3 mJy, 
not the +/- 0.08 mJy, 
which is only the raw rms in the unsubtracted data.

This means the 2mm continuum "detection" of the lensed arc (Fig.4 upper)
may not be real. 
On the map in Fig.4, it is only a bend in the lowest contour (3-sigma), 
so not really significant.

It might be better to rewrite Sect.3.3, para.2 to say something like:

"We detect 2mm continuum with an integrated flux density of 1.2+/-0.2 mJy,
with a peak flux of 0.80+/-0.09 mJy/beam, centered on the lensing galaxy.
In the lowest contour (3-sigma), there is a hint of possible emission
from the lensed arc."

Instead of calling this the "deblending procedure",
which people might confuse with deconvolution, 
I would just call it "subtraction of the foreground galaxy", 
or "flux removal by subtraction", because it is just simple 
subtraction, not anything else.

# RESPONSE
We updated the 2mm flux in Table 1. We updated the flux uncertainty to include those from the uv-fitting process.

@@

The peak emission in the residual map is 0.39 +/- 0.08 mJy. While the uncertainty associated with the flux measurement of the background source needs to propagate the errors from subtracting the fitted model flux, the significance of the emission in the residual doesn't not. It simply is Data-Model, which is > 4 sigma than the noise. This together with the co-spatial emission supports that flux contributiion from the background source to the total integrated 2mm continuum.

The term "deblending" is a broadly used in photometry, and it is clear that it refers to the flux subtraction within the same paragraph. We therefore make no changes to the wording.

6) DROP THE SPECTRAL INDEX FOR THE BACKGROUND GALAXY :

Sect.3.3, para.3:

Given the large uncertainty in the residual flux, I don't think
you can derive a 6cm-to-2mm spectral index for the background galaxy.
I suggest dropping that part of the sentence:
(" alpha = -0.345 for the background galaxy ")

### 2016-11-22 WRITEUP/ms.tex
revised with DR's comments

\citestyle{aa}
\shorttitle{Molecular Gas Kinematics of the Strongly-lensed Quasar Host Galaxy RXJ1131$-$1231}
\shortauthors{Leung, Riechers \& Pavesi}

@@

\title{Molecular Gas Kinematics of the Strongly-lensed Quasar Host Galaxy RXS J1131$-$1231}
\author{T. K. Daisy Leung, Dominik A. Riechers, and Riccardo Pavesi}
\affil{Department of Astronomy, Space Sciences Building, Cornell University,
Ithaca, NY 14853, USA; \myemail}

@@

\begin{abstract}
We report observations of \bco and \cco line emission towards
the quadruply-lensed quasar
RXS\,J1131$-$1231 at $z$\,=\,0.654 obtained using the
\pdbi (PdBI) and the \carma (CARMA).
Our lens modeling shows that the asymmetry in the double-horned \bco line profile
is mainly a result of differential lensing, where
the magnification factor varies from $\sim$3 to $\sim$9 across
different kinematic components.
The intrinsically symmetric line profile with a conspicuous source-plane velocity
gradient suggests that
the host galaxy is an extended rotating disk, with a CO size of $R_{\rm CO}$$\sim$6\,kpc and
a dynamical mass of $M_{\rm dyn}$\ssim8\E{10}\,\Msun.
In addition, we find a secondary CO-emitting source near RXS\,J1131$-$1231 whose location is
consistent with the optically-faint companion reported in previous studies.
The lensing-corrected molecular gas masses are $M_{\rm gas}$\ssim1.4\E{10}\,\Msun
and \ssim2\E{9}\,\Msun for RXS\,J1131$-$1231 and the companion, respectively.
The gas mass fraction of $\sim$18\% inferred for RXS\,J1131$-$1231 is consistent with the trend of decreasing molecular gas fraction since $z$\ssim2 reported in recent studies.
We find lensing-corrected stellar and dust masses, an IR luminosity, and a
star formation rate of
$M_{*}$\ssim3\E{10}\,\Msun, $M_{\rm dust}$\ssim3\E{8}\,\Msun, $L_{\rm IR}$\ssim1.5\E{12}\,\Lsun,  and SFR$_{\rm FIR}$\ssim120\,\sfrU for RXS\,J1131$-$1231.
The source-plane morphologies of its gas and stellar populations
indicate that the star-formation activity may be as extended as the molecular gas reservoir.
We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of $>$0.27\petm{0.11}{0.08}\% which is higher
than the 
local value, suggesting that the bulk of the black hole mass of RXSJ1131-1231 is largely in place while its stellar bulge is still assembling.
\end{abstract}

@@

\defcitealias{Sluse03a}{S03}
The quasar RXS J113151.62$-$123158 (hereafter RXJ1131)
at $z_\textrm{s, QSO}$\eq$0.685$ \citep[hereafter S03]{Sluse03a} is a particularly well-suited source for
studying the evolution of molecular gas properties in quasar host galaxies and the
connection between SMBHs and their host galaxies at intermediate redshift
given its unique lensing configuration.
The stellar emission in the host galaxy of RXJ1131 is lensed into
an Einstein ring of $1$\farcs$83$ in radius
that is clearly separated from the quadruply imaged quasar emission \citep[hereafter C06]{Claeskens06a}.
The foreground lens is an elliptical galaxy at $z_\textrm{L}$\eq$0.295$ \citepalias{Sluse03a}.
 \citet[][]{Reis14a} report a high spin parameter of $a$\,$\sim$\,$0.9$ for the moderate-mass black hole in RXJ1131 \citep[$M_{\rm BH}$\eq$8$\E{7}\Msun;][]{Sluse12a}, %based on H beta line
with an intrinsic bolometric luminosity of $L_{\rm bol, X}$\eq$1.3$\E{45}\, ergs\,s\pmOne \citep{Pooley07a}.

@@

%--------------------------------------------------------------------------
%                          Observations details
%--------------------------------------------------------------------------
\section{Observations} \label{sec:obs}
\subsection{PdBI \bco}
Observations of the \bco rotational line
($\nu_{\rm rest}$\,=\,$230.53800$ GHz) at the tuning frequency of 
$\nu_{\rm obs}$\eq139.256\,GHz
% redshifted to $\nu_{\rm obs}$\eq139.40739\,GHz
were carried out using IRAM \pdbi (PdBI; Program ID: S14BX; PI: D.
Riechers). Two observing runs were carried out on 2014 December 06 and 2015
February 05 under good weather conditions in the C and D array configurations,
respectively.
This resulted in 3.75 hours of cumulative six antenna-equivalent on-source
 time after discarding unusable visibility data.
The 2 mm receivers were used to cover the redshifted \bco line
and the underlying continuum emission, employing a correlator setup that provides
an effective bandwidth of 3.6 GHz (dual polarization) and a native spectral resolution of 1.95\,MHz
($\sim$\,$4.2$\,\kms).
The nearby quasars B1127$-$145 and B1124$-$186 were observed every 22 minutes
for pointing, secondary amplitude, and phase calibration, and B1055$+$018 was
observed as the bandpass calibrator for both tracks.
MWC349 and 3C279 were observed as primary flux calibrators for the C and D
array observations, respectively, yielding calibration accuracy better than 15\%.

\subsection{CARMA \cco}
Observations of the \cco rotational line in RXJ1131
($\nu_{\rm rest}$\,=\,345.79599\,GHz) 
% redshifted to 
at the observe frequency of $\nu_{\rm obs}$\eq209.10443\,GHz    % i.e. where we thought the line was redshifted to 
were carried out with the \carma (CARMA;
Program ID: cf0098; PI: D. Riechers)
in the D array configuration on 2014 February 02 under poor 1.5\,mm
weather conditions and on 2014 February 17 under good 1.5\,mm
weather conditions.
This resulted in a total on-source time of 2.94 hours after flagging poor
visibility data.
The correlator setup provides a bandwidth of 3.75 GHz in
each sideband and a %native
spectral resolution of 12.5 MHz ($\sim$17.9 \kms). The
line was placed in the lower sideband with the local oscillator tuned to $\nu_{\rm LO}\sim$216 GHz. The radio quasars J1127$-$189 (first track) and 3C273
(second track) were observed
every 15 minutes for pointing, amplitude, and phase calibration. Mars was
observed as the primary absolute flux calibrator and 3C279 was observed as
the bandpass calibrator for both tracks.

@@

@@

%--------------------------------------------------------------------------
%                                Results
%--------------------------------------------------------------------------
\section{Results} \label{sec:results}
The observed properties of \bco and \cco emission are summarized in \Tab{obsprop}.
\input{table_obsprop}

\subsection{\bco Emission} \label{sec:CO21}
We detect \bco line emission toward the background source in the PdBI data
at $\gtrsim$\,27$\sigma$ significance, enabling us to constrain its redshift at 
$z_{\rm CO}$\eq0.6541\,$\pm$\,0.0002\footnote{This redshift is derived by fitting a double-Gaussian to 
the de-lensed spectrum, which is shown in \Fig{delensed}.
% instead of the observed spectrum (\Fig{CO21spec}) to avoid biases in our 
% redshift determination of the dynamical center due to differential lensing (see \Sec{differential}).
}. The emission is spatially and kinematically resolved
with a highly asymmetric double-horned line profile
as shown in \Fig{CO21spec}. Fitting a double Gaussian results in peak
flux densities of 75.3\pmm2.6 mJy and 24.0\pmm2.0 mJy, and a FWHM of
179\pmm9 \kms and 255\pmm28 \kms for the two components, respectively. The peaks are separated by
$\Delta v_{\rm sep}$\eq400\pmm12\,\kms. The total integrated line flux is 20.3\,$\pm$\,0.6 Jy \kms. % see 15May16/

>>>>

\citestyle{aa}
\shorttitle{Molecular Gas Kinematics of the Strongly-Lensed Quasar Host Galaxy RXJ1131$-$1231}
\shortauthors{Leung, Riechers \& Pavesi}

@@

\title{Molecular Gas Kinematics of the Strongly-Lensed Quasar Host Galaxy RXS J1131$-$1231}
\author{T. K. Daisy Leung, Dominik A. Riechers, and Riccardo Pavesi}
\affil{Department of Astronomy, Space Sciences Building, Cornell University,
Ithaca, NY 14853, USA; \myemail}

@@

\begin{abstract}
We report observations of \bco and \cco line emission towards
the quadruply-lensed quasar
RXS\,J1131$-$1231 at $z$\,=\,0.654 obtained using the
\pdbi (PdBI) and the \carma (CARMA).
Our lens modeling shows that the asymmetry in the double-horned \bco line profile
is mainly a result of differential lensing, where
the magnification factor varies from $\sim$3 to $\sim$9 across
different kinematic components.
The intrinsically symmetric line profile with a conspicuous source-plane velocity
gradient suggests that
the host galaxy is an extended rotating disk, with a CO size of $R_{\rm CO}$$\sim$6\,kpc and
a dynamical mass of $M_{\rm dyn}$\ssim8\E{10}\,\Msun.
In addition, we find a secondary CO-emitting source near RXS\,J1131$-$1231 whose location is
consistent with the optically-faint companion reported in previous studies.
The lensing-corrected molecular gas masses are $M_{\rm gas}$\eq(1.4\pmm0.3)\E{10}\,\Msun
and (2.0\pmm0.1)\E{9}\,\Msun for RXS\,J1131$-$1231 and the companion, respectively.
The gas mass fraction of $f_{\rm gas}$\eq18\pmm4\% inferred for RXS\,J1131$-$1231 is consistent with the trend of decreasing molecular gas fraction since $z$\ssim2 reported in recent studies.
We find lensing-corrected stellar and dust masses, an IR luminosity, and a
star formation rate of
$M_{*}$\eq(3\pmm1)\E{10}\,\Msun, $M_{\rm dust}$\ssim3\E{8}\,\Msun, $L_{\rm IR}$\ssim1.5\E{12}\,\Lsun,  and SFR$_{\rm FIR}$\eq(120\pmm63)\,\sfrU for RXS\,J1131$-$1231.
The source-plane morphologies of its gas and stellar populations
indicate that the star-formation activity may be as extended as the molecular gas reservoir.
We find a $M_{\rm BH}$$/$$M_{\rm bulge}$ ratio of $>$0.27\petm{0.11}{0.08}\% which is higher
than the 
local value, suggesting that the bulk of the black hole mass of RXSJ1131-1231 is largely in place while its stellar bulge is still assembling.
\end{abstract}

@@

\defcitealias{Sluse03a}{S03}
The quasar RXS J113151.62$-$123158 (hereafter RXJ1131)
at $z_\textrm{s, QSO}$\eq$0.658$ \citep[hereafter S03]{Sluse03a} is a particularly well-suited source for
studying the evolution of molecular gas properties in quasar host galaxies and the
connection between SMBHs and their host galaxies at intermediate redshift
given its unique lensing configuration.
The stellar emission in the host galaxy of RXJ1131 is lensed into
an Einstein ring of $1$\farcs$83$ in radius
that is clearly separated from the quadruply imaged quasar emission \citep[hereafter C06]{Claeskens06a}.
The foreground lens is an elliptical galaxy at $z_\textrm{L}$\eq$0.295$ \citepalias{Sluse03a}.
 \citet[][]{Reis14a} report a high spin parameter of $a$\,$\sim$\,$0.9$ for the moderate-mass black hole in RXJ1131 \citep[$M_{\rm BH}$\eq$8$\E{7}\Msun;][]{Sluse12a}, %based on H beta line
with an intrinsic bolometric luminosity of $L_{\rm bol, X}$\eq$1.3$\E{45}\, ergs\,s\pmOne \citep{Pooley07a}.

@@

%--------------------------------------------------------------------------
%                          Observations details
%--------------------------------------------------------------------------
\section{Observations} \label{sec:obs}

\subsection{CARMA \cco}
Observations of the \cco rotational line 
($\nu_{\rm rest}$\,=\,345.79599\,GHz) redshifted to $\nu_{\rm obs}$\eq209.10443\,GHz
towards RXJ1131 at $z_{\rm QSO}$\eq0.658 
were carried out with the \carma (CARMA;
Program ID: cf0098; PI: D. Riechers) in the D array configuration. They were carried out
on 2014 February 02 under poor 1.5\,mm
weather conditions and on 2014 February 17 under good 1.5\,mm
weather conditions.
This resulted in a 
total on-source time of 2.94 hours after flagging poor
visibility data.
The correlator setup provides a bandwidth of 3.75 GHz in
each sideband and a %native
spectral resolution of 12.5 MHz ($\sim$17.9 \kms). The
line was placed in the lower sideband with the local oscillator tuned to $\nu_{\rm LO}\sim$216 GHz. The radio quasars J1127$-$189 (first track) and 3C273
(second track) were observed
every 15 minutes for pointing, amplitude, and phase calibration. Mars was
observed as the primary absolute flux calibrator and 3C279 was observed as
the bandpass calibrator for both tracks.

@@

\subsection{PdBI \bco}
Observations of the \bco rotational line
($\nu_{\rm rest}$\,=\,$230.53800$ GHz) 
redshifted to $\nu_{\rm obs}$\eq139.256\,GHz towards RXJ1131
at the
CARMA \cco redshift of $z_{\rm CO(3-2)}$\eq0.655
were carried out using IRAM \pdbi (PdBI; Program ID: S14BX; PI: D.
Riechers).
Two observing runs were carried out on 2014 December 06 and 2015
February 05 under good weather conditions in the C and D array configurations,
respectively.
This resulted in 3.75 hours of cumulative six antenna-equivalent on-source
 time after discarding unusable visibility data.
The 2 mm receivers were used to cover the redshifted \bco line
and the underlying continuum emission, employing a correlator setup that provides
an effective bandwidth of 3.6 GHz (dual polarization) and a native spectral resolution of 1.95\,MHz
($\sim$\,$4.2$\,\kms).
The nearby quasars B1127$-$145 and B1124$-$186 were observed every 22 minutes
for pointing, secondary amplitude, and phase calibration, and B1055$+$018 was
observed as the bandpass calibrator for both tracks.
MWC349 and 3C279 were observed as primary flux calibrators for the C and D
array observations, respectively, yielding calibration accuracy better than 15\%.

@@

%--------------------------------------------------------------------------
%                                Results
%--------------------------------------------------------------------------
\section{Results} \label{sec:results}
\input{table_obsprop}

\subsection{\bco Emission} \label{sec:CO21}
We detect \bco line emission towards the background source RXJ1131 in the PdBI data
at $\gtrsim$\,27$\sigma$ significance. Based on this measurement, we refine the redshift of RXJ1131 to
$z_{\rm CO}$\eq0.6541\,$\pm$\,0.0002\footnote{This redshift is derived by fitting a double-Gaussian to 
the de-lensed spectrum (\Fig{delensed}) 
instead of the observed spectrum (\Fig{CO21spec}) to avoid biases in our 
redshift determination 
due to differential lensing (see \Sec{differential}).
}. The emission is spatially and kinematically resolved
with a highly asymmetric double-horned line profile
as shown in \Fig{CO21spec}. Fitting a double Gaussian results in peak
flux densities of 75.3\pmm2.6 mJy and 24.0\pmm2.0 mJy, and a FWHM of
179\pmm9 \kms and 255\pmm28 \kms for the two components, respectively. The peaks are separated by
$\Delta v_{\rm sep}$\eq400\pmm12\,\kms. The total integrated line flux is 20.3\,$\pm$\,0.6 Jy \kms. % see 15May16/

\begin{figure}[htbp]
\centering
\includegraphics[width=0.45\textwidth]{../Figures/SpecCO21_twinx.eps}
\caption{Continuum-subtracted spectrum (histogram) of \bco emission towards RXJ1131, with a spectral resolution of
22\,\kms. The solid black line shows a double-Gaussian fit to the line profile.
The velocity scale is with respect to $z$\,=\,0.6541, which corresponds to the line center of RXJ1131 based on
the de-lensed line profile (\Fig{delensed}).
A detailed discussion of this effect is presented in \Sec{differential}. \label{fig:CO21spec}}
\end{figure}
\vspace{.2em}
% moment 0 map, highest SNR: CASA chan=125~159 <=> GILDAS 126-160 <=> python 125-160
% - sigma = 0.305 Jy km/s/Beam
%   - note that theoretical sigma is lower = 1.5 * sqrt(160-126+1) * 21.5 ~ 0.2 Jy km/s /beam, due to higher noise in some channels with emission
We construct a zeroth order moment map, red/blue channel maps, and
first and second moment maps, as shown in \Fig{CO21mom},
using the $uv$-continuum subtracted data cube over a velocity range of
$\Delta v$ $\sim$ 750\,\kms.
The higher-order moment maps are produced using
unbinned channel maps with 3$\sigma$ clipping.
The peak flux density is 8.12\pmm0.30 Jy\,\kms\,beam\pmOne
in the intensity map.
Observed properties of the \bco emission line are summarized in \Tab{obsprop}.
